---
title: "Mechanism knockout analyses"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mechanism knockout analyses}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview

Mechanism knockouts allow users to evaluate how individual model components affect simulated community assembly. Here, we switch off individual modules (e.g., spatial layering, host sanctions) to quantify each mechanism’s contribution relative to the baseline configuration modeling (BCM).

Run a set of reduced model configurations to test the necessity of specific intrinsic mechanisms.
Each entry modifies one key mechanism in the baseline configuration modeling (BCM) while keeping other parameters fixed.
we need remove the figs labeled as "dropped" from the final dataset.

```{r mechanism_knockouts}

library(figsimR)
library(dplyr)
library(forcats)
library(ggplot2)
library(scales)
library(DiagrammeR)
library(vegan)
library(patchwork)
library(purrr)
library(stringr)
library(tibble)
library(readr)
library(ggpubr)
library(Hmsc)       
library(future)     
library(progressr)  
library(tidyr)

set.seed(42)

data("observed_data")
data("species_list")
data("parameter_list_default")

lhs_optimize_result <- readRDS(system.file("extdata", "lhs_optimize_result.rds", package = "figsimR"))

# Extract the single best-performing parameter row (minimum loss)
# Rebuild the full parameter list object from the best result row
lhs_optimize_parameter <- rebuild_parameter_list_from_row(lhs_optimize_result[1, ],
                                                          parameter_list_default)
														  
BCM_reduced_results <- list(
  # basic BCM
  run_fim_reduced_experiment("BCM", lhs_optimize_parameter, species_list),
  # Remove spatial layering
  run_fim_reduced_experiment("BCM_No_space", lhs_optimize_parameter,species_list, use_layering = FALSE, use_layer_preference = FALSE),
  # Remove layer preference
  run_fim_reduced_experiment("BCM_No_layer_preference", lhs_optimize_parameter, species_list, use_layering = TRUE, use_layer_preference = FALSE),
  # Disable host sanctioning
  run_fim_reduced_experiment("BCM_No_sanction",lhs_optimize_parameter, species_list, enable_drop = FALSE,host_sanction = 1),
  # enable sink strength and disable host sanctioning
  run_fim_reduced_experiment("BCM_sink_strength_2_95", lhs_optimize_parameter, species_list, enable_drop = FALSE, use_sink_strength = TRUE,
                                  sink_min_prop = 0.20, sink_max_prop = 0.95, sink_controls_drop = TRUE, sink_drop_condition = "outside_range"),

  # Remove phenological effects
  run_fim_reduced_experiment("BCM_No_temporal", lhs_optimize_parameter, species_list, use_egg_success_by_phase = FALSE)
)


# Combine the outputs from each model variant into a single data frame
metrics_reduced_models <- bind_rows(BCM_reduced_results)
head(metrics_reduced_models)

# resample observed data and calculate metrics
file_path <- system.file("extdata", "resample_observed_metrics_df_results.rds", package = "figsimR")

if (file_path != "" && file.exists(file_path)) {
  message("Loading precomputed resampled simulated result...")
  resample_observed_metrics_df_results <- readRDS(file_path)
} else {
  message("Running resampling may take several minutes...")
  resample_observed_metrics_df_results  <- resample_observed_all_metrics(
  observed_df = observed_data,       # empirical data
  seed = 42,                         # set seed for reproducibility
  wasp_cols = species_list,          # columns corresponding to species counts
  n_draws = 500,                     # number of bootstrap replicates
  sample_n = 200,                    # number of figs sampled per replicate
  calc_func = calc_all_metrics       # metric calculation function
  )
}

head(resample_observed_metrics_df_results)

# Summary statistics across all bootstrap replicates
summary(resample_observed_metrics_df_results )

metrics_keep <- c("mean_richness", "mean_evenness", "mean_bray_curtis",
                  "connectance", "nestedness", "modularity")


# observed data matrics
bootstrap_metrics_observed <- resample_observed_metrics_df_results %>%
  select(all_of(metrics_keep))

bootstrap_metrics_observed$Source <- "Observed"

colnames(bootstrap_metrics_observed) <- c("Richness", "Pielou's Evenness", "Bray-Curtis Dissimilarity",
                                          "Nestedness", "Connectance", "Modularity","Source")

# delta coverage & delta loss


# ---------- 0) clean data  ----------
metric_cols <- c("Richness","Pielou's Evenness","Bray-Curtis Dissimilarity",
                 "Nestedness","Connectance","Modularity")

#  KO + BCM
sim_boot <- metrics_reduced_models %>%
  select(all_of(metric_cols), Source)

#
obs_boot <- bootstrap_metrics_observed %>%
  select(all_of(metric_cols), Source)

#
unique(sim_boot$Source)
# "BCM", "BCM_No_space", "BCM_No_layer_preference", "BCM_No_sanction", "BCM_sink_strength_2_95", "BCM_No_temporal"

# ---------- 1) ΔLoss （BCM）----------
# Loss(M) = sum_i ( mean_sim_i(M) - mean_obs_i )^2

obs_means <- obs_boot %>%
  select(all_of(metric_cols)) %>%
  pivot_longer(everything(), names_to="metric", values_to="val") %>%
  group_by(metric) %>% summarise(obs_mu = mean(val), .groups="drop")

sim_means <- sim_boot %>%
  select(all_of(metric_cols), Source) %>%
  pivot_longer(cols = all_of(metric_cols), names_to="metric", values_to="val") %>%
  group_by(Source, metric) %>%
  summarise(sim_mu = mean(val), .groups="drop")

loss_by_model <- sim_means %>%
  inner_join(obs_means, by="metric") %>%
  group_by(Source) %>%
  summarise(Loss = sum((sim_mu - obs_mu)^2), .groups="drop")

Loss_BCM <- loss_by_model %>% filter(Source == "BCM") %>% pull(Loss)

delta_loss <- loss_by_model %>%
  filter(Source != "BCM") %>%
  mutate(dLoss = Loss - Loss_BCM) %>%
  select(Source, dLoss)


# ---------- 2) ΔCoverage（pp， BCM）----
q_levels <- c(0.05, 0.25, 0.50, 0.75, 0.95)


#
obs_q <- obs_boot |>
  dplyr::select(dplyr::all_of(metric_cols)) |>
  tidyr::pivot_longer(everything(), names_to="metric", values_to="val") |>
  dplyr::group_by(metric) |>
  dplyr::summarise(
    `5%`  = quantile(val, 0.05, type=8),
    `25%` = quantile(val, 0.25, type=8),
    `50%` = quantile(val, 0.50, type=8),
    `75%` = quantile(val, 0.75, type=8),
    `95%` = quantile(val, 0.95, type=8),
    .groups="drop"
  ) |>
  tidyr::pivot_longer(-metric, names_to="q_lab", values_to="obs_qval") |>
  dplyr::mutate(q = readr::parse_number(q_lab)/100)


env_BCM   <- envelope_for_model(sim_boot |> dplyr::filter(Source=="BCM"), metric_cols, B=1000)
marg_BCM  <- mean_exceed_norm(env_BCM, obs_q)


sources_KO <- setdiff(unique(sim_boot$Source), "BCM")

delta_cov_cont <- purrr::map_dfr(sources_KO, function(src){
  env_KO  <- envelope_for_model(sim_boot |> dplyr::filter(Source==src), metric_cols, B=1000)
  marg_KO <- mean_exceed_norm(env_KO, obs_q)
  tibble::tibble(Source = src, dCov_cont = marg_KO - marg_BCM)
})


#community data

sim_BCM <- simulate_figwasp_community(
  num_figs                 = 1000,
  fecundity_mean           = lhs_optimize_parameter$fecundity_mean,
  fecundity_dispersion     = lhs_optimize_parameter$fecundity_dispersion,
  entry_mu                 = lhs_optimize_parameter$entry_mu,
  entry_size               = lhs_optimize_parameter$entry_size,
  entry_priority           = lhs_optimize_parameter$entry_priority,
  species_roles            = lhs_optimize_parameter$species_roles,
  max_entry_table          = lhs_optimize_parameter$max_entry_table,
  enable_drop              = TRUE,
  drop_cancels_emergence   = FALSE,
  entry_distribution       = "lognormal",
  interaction_matrix       = lhs_optimize_parameter$interaction_matrix,
  interaction_weight       = 0,
  egg_success_prob_by_phase= lhs_optimize_parameter$egg_success_prob_by_phase,
  layer_preference         = lhs_optimize_parameter$layer_preference,
  seed                     = 42
)

sim_BCM <- sim_BCM$summary
dim(sim_BCM)
sim_BCM <- sim_BCM[sim_BCM$is_dropped != 1, ]
dim(sim_BCM)
sim_BCM <- sim_BCM[,c(18:23)]
colnames(sim_BCM) <- gsub("^emergence_", "", colnames(sim_BCM))


obs_comm_mat <- observed_data

sim_BCM <- sim_BCM[, match(colnames(obs_comm_mat), colnames(sim_BCM))]


# KO: sim_KO_space
sim_KO_space <- simulate_figwasp_community(
  num_figs                 = 1000,
  fecundity_mean           = lhs_optimize_parameter$fecundity_mean,
  fecundity_dispersion     = lhs_optimize_parameter$fecundity_dispersion,
  entry_mu                 = lhs_optimize_parameter$entry_mu,
  entry_size               = lhs_optimize_parameter$entry_size,
  entry_priority           = lhs_optimize_parameter$entry_priority,
  species_roles            = lhs_optimize_parameter$species_roles,
  max_entry_table          = lhs_optimize_parameter$max_entry_table,
  enable_drop              = TRUE,
  drop_cancels_emergence   = FALSE,
  entry_distribution       = "lognormal",
  interaction_matrix       = lhs_optimize_parameter$interaction_matrix,
  interaction_weight       = 0,
  egg_success_prob_by_phase= lhs_optimize_parameter$egg_success_prob_by_phase,
  layer_preference         = lhs_optimize_parameter$layer_preference,
  use_layering             = FALSE,
  use_layer_preference     = FALSE,
  seed                     = 42
)

sim_KO_space <- sim_KO_space$summary
dim(sim_KO_space)
sim_KO_space <- sim_KO_space[sim_KO_space$is_dropped != 1, ]
dim(sim_KO_space)
sim_KO_space <- sim_KO_space[,c(18:23)]
colnames(sim_KO_space) <- gsub("^emergence_", "", colnames(sim_KO_space))
sim_KO_space <- sim_KO_space[, match(colnames(obs_comm_mat), colnames(sim_KO_space))]

# No layer preference
sim_No_layer_preference <- simulate_figwasp_community(
  num_figs                 = 1000,
  fecundity_mean           = lhs_optimize_parameter$fecundity_mean,
  fecundity_dispersion     = lhs_optimize_parameter$fecundity_dispersion,
  entry_mu                 = lhs_optimize_parameter$entry_mu,
  entry_size               = lhs_optimize_parameter$entry_size,
  entry_priority           = lhs_optimize_parameter$entry_priority,
  species_roles            = lhs_optimize_parameter$species_roles,
  max_entry_table          = lhs_optimize_parameter$max_entry_table,
  enable_drop              = TRUE,
  drop_cancels_emergence   = FALSE,
  entry_distribution       = "lognormal",
  interaction_matrix       = lhs_optimize_parameter$interaction_matrix,
  interaction_weight       = 0,
  egg_success_prob_by_phase= lhs_optimize_parameter$egg_success_prob_by_phase,
  layer_preference         = lhs_optimize_parameter$layer_preference,
  use_layering             = TRUE,
  use_layer_preference     = FALSE,
  seed                     = 42
)

sim_No_layer_preference <- sim_No_layer_preference$summary
dim(sim_No_layer_preference)
sim_No_layer_preference <- sim_No_layer_preference[sim_No_layer_preference$is_dropped != 1, ]
dim(sim_No_layer_preference)
sim_No_layer_preference <- sim_No_layer_preference[,c(18:23)]
colnames(sim_No_layer_preference) <- gsub("^emergence_", "", colnames(sim_No_layer_preference))
sim_No_layer_preference <- sim_No_layer_preference[, match(colnames(obs_comm_mat), colnames(sim_No_layer_preference))]

# KO: sim_KO_sanction
sim_KO_sanction <- simulate_figwasp_community(
  num_figs                 = 1000,
  fecundity_mean           = lhs_optimize_parameter$fecundity_mean,
  fecundity_dispersion     = lhs_optimize_parameter$fecundity_dispersion,
  entry_mu                 = lhs_optimize_parameter$entry_mu,
  entry_size               = lhs_optimize_parameter$entry_size,
  entry_priority           = lhs_optimize_parameter$entry_priority,
  species_roles            = lhs_optimize_parameter$species_roles,
  max_entry_table          = lhs_optimize_parameter$max_entry_table,
  enable_drop              = FALSE,
  drop_cancels_emergence   = FALSE,
  entry_distribution       = "lognormal",
  interaction_matrix       = lhs_optimize_parameter$interaction_matrix,
  interaction_weight       = 0,
  egg_success_prob_by_phase= lhs_optimize_parameter$egg_success_prob_by_phase,
  layer_preference         = lhs_optimize_parameter$layer_preference,
  host_sanction            = 1,
  seed                     = 42
)

sim_KO_sanction <- sim_KO_sanction$summary
dim(sim_KO_sanction)
sim_KO_sanction <- sim_KO_sanction[sim_KO_sanction$is_dropped != 1, ]
dim(sim_KO_sanction)
sim_KO_sanction <- sim_KO_sanction[,c(18:23)]
colnames(sim_KO_sanction) <- gsub("^emergence_", "", colnames(sim_KO_sanction))
sim_KO_sanction <- sim_KO_sanction[, match(colnames(obs_comm_mat), colnames(sim_KO_sanction))]

# enable: sink strength
sim_en_strength <- simulate_figwasp_community(
  num_figs                 = 1000,
  fecundity_mean           = lhs_optimize_parameter$fecundity_mean,
  fecundity_dispersion     = lhs_optimize_parameter$fecundity_dispersion,
  entry_mu                 = lhs_optimize_parameter$entry_mu,
  entry_size               = lhs_optimize_parameter$entry_size,
  entry_priority           = lhs_optimize_parameter$entry_priority,
  species_roles            = lhs_optimize_parameter$species_roles,
  max_entry_table          = lhs_optimize_parameter$max_entry_table,
  enable_drop              = FALSE,
  drop_cancels_emergence   = FALSE,
  entry_distribution       = "lognormal",
  interaction_matrix       = lhs_optimize_parameter$interaction_matrix,
  interaction_weight       = 0,
  egg_success_prob_by_phase= lhs_optimize_parameter$egg_success_prob_by_phase,
  layer_preference         = lhs_optimize_parameter$layer_preference,
  use_layering             = FALSE,
  use_layer_preference     = FALSE,
  use_sink_strength        = TRUE,
  sink_min_prop            = 0.20,
  sink_max_prop            = 0.95,
  seed                     = 42
)

sim_en_strength <- sim_en_strength$summary
dim(sim_en_strength)
sim_en_strength <- sim_en_strength[!(sim_en_strength$sink_below_min | sim_en_strength$sink_above_max), ]
any(sim_en_strength$sink_below_min | sim_en_strength$sink_above_max)
dim(sim_en_strength)
sim_en_strength <- sim_en_strength[,c(18:23)]
colnames(sim_en_strength) <- gsub("^emergence_", "", colnames(sim_en_strength))
sim_en_strength <- sim_en_strength[, match(colnames(obs_comm_mat), colnames(sim_en_strength))]


# KO: sim_KO_temporal
sim_KO_temporal <- simulate_figwasp_community(
  num_figs                 = 1000,
  fecundity_mean           = lhs_optimize_parameter$fecundity_mean,
  fecundity_dispersion     = lhs_optimize_parameter$fecundity_dispersion,
  entry_mu                 = lhs_optimize_parameter$entry_mu,
  entry_size               = lhs_optimize_parameter$entry_size,
  entry_priority           = lhs_optimize_parameter$entry_priority,
  species_roles            = lhs_optimize_parameter$species_roles,
  max_entry_table          = lhs_optimize_parameter$max_entry_table,
  enable_drop              = TRUE,
  drop_cancels_emergence   = FALSE,
  entry_distribution       = "lognormal",
  interaction_matrix       = lhs_optimize_parameter$interaction_matrix,
  interaction_weight       = 0,
  egg_success_prob_by_phase= lhs_optimize_parameter$egg_success_prob_by_phase,
  layer_preference         = lhs_optimize_parameter$layer_preference,
  use_egg_success_by_phase = FALSE,
  seed                     = 42
)

sim_KO_temporal <- sim_KO_temporal$summary
dim(sim_KO_temporal)
sim_KO_temporal <- sim_KO_temporal[sim_KO_temporal$is_dropped != 1, ]
dim(sim_KO_temporal)
sim_KO_temporal <- sim_KO_temporal[,c(18:23)]
colnames(sim_KO_temporal) <- gsub("^emergence_", "", colnames(sim_KO_temporal))
sim_KO_temporal <- sim_KO_temporal[, match(colnames(obs_comm_mat), colnames(sim_KO_temporal))]

# Estimate observed-to-simulated dispersion ratio by matched resampling
rho_BCM   <- compute_rho_matched_fast(obs_comm_mat, sim_BCM, reps = 200)
rho_space <- compute_rho_matched_fast(obs_comm_mat, sim_KO_space, reps = 200)
rho_prefer <- compute_rho_matched_fast(obs_comm_mat, sim_No_layer_preference, reps = 200)
rho_sanc  <- compute_rho_matched_fast(obs_comm_mat, sim_KO_sanction, reps = 200)
rho_sink <- compute_rho_matched_fast(obs_comm_mat, sim_en_strength, reps = 200)
rho_temp  <- compute_rho_matched_fast(obs_comm_mat, sim_KO_temporal, reps = 200)



dRho_tbl <- tibble(
  Source   = c("BCM_No_space", "BCM_No_layer_preference", "BCM_No_sanction", "BCM_sink_strength_2_95", "BCM_No_temporal"),
  dRho_pct = c(100*(rho_space["mean"]/rho_BCM["mean"]-1),
               100*(rho_prefer["mean"]/rho_BCM["mean"]-1),
               100*(rho_sanc["mean"]/rho_BCM["mean"]-1),
               100*(rho_sink["mean"]/rho_BCM["mean"]-1),
               100*(rho_temp["mean"]/rho_BCM["mean"]-1))
)



# plotting

fig_summary <- delta_loss |>
  dplyr::inner_join(delta_cov_cont, by="Source") |>
  dplyr::inner_join(dRho_tbl,     by="Source") |>
  dplyr::mutate(
    label = dplyr::recode(Source,
                          BCM_No_space    = "KO: Spatial partitioning",
                          BCM_No_layer_preference = "Disable: Layer preference",
                          BCM_No_sanction = "KO: Host sanctions",
                          BCM_sink_strength_2_95 = "Enable: Sink strength",
                          BCM_No_temporal = "KO: Phase-specific success"
    ),
    zLoss = scale_safe(dLoss),
    zCov  = scale_safe(dCov_cont),
    rank_score = abs(zLoss) + abs(zCov)
  ) |>
  dplyr::arrange(dplyr::desc(rank_score)) |>
  dplyr::mutate(label = factor(label, levels = label))

# Panel A: ΔLoss
fg_panela <- ggplot(fig_summary, aes(x = dLoss, y = label)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_col(fill = "#5DADE2", width = 0.4) +
  #scale_x_continuous(labels = label_number(accuracy = 1)) +
  scale_x_continuous(labels = label_number(big.mark=",")) +
  labs(
    #title = "A. Impact on Mean Fit (ΔLoss)",
    x = "Change in total loss relative to BCM",
    y = NULL
  ) +
  theme_classic(base_size = 9, base_family = "Arial") +
  theme(
    plot.title = element_text(face = "bold"),
    axis.title.x = element_text(margin = margin(t = 6))
  )

# Panel B: ΔCoverage

fg_panelb <- ggplot(fig_summary, aes(x = dRho_pct, y = label)) +
  geom_vline(
    xintercept = 0,
    linetype = "dashed",
    color = "grey60"
  ) +
  geom_col(
    fill = "#F5B041",
    width = 0.4
  ) +
  geom_text(
    aes(
      x = dRho_pct * 0.6,
      label = sprintf("Δρ = %.2f%%", dRho_pct)
    ),
    position = position_nudge(y = 0.30),
    hjust = ifelse(fig_summary$dRho_pct >= 0, 0, 1),
    vjust = 0.5,
    size = 2.5
  ) +
  labs(
    x = "Change in dispersion ratio, Δρ (%) relative to BCM",
    y = NULL
  ) +
  coord_cartesian(clip = "off") +
  theme_classic(base_size = 9, base_family = "Arial") +
  theme(
    axis.title.x = element_text(margin = margin(t = 6)),
    plot.margin = margin(t = 5, r = 25, b = 5, l = 5)
  )

fg_panelb


figure <- fg_panela + fg_panelb + plot_layout(ncol = 2, nrow = 2, widths = c(1, 1.1)) +
  plot_annotation(tag_levels = 'A')

figure


sim_cases_list <- list(
  BCM              = sim_BCM,
  KO_space         = sim_KO_space,
  No_layer_preference = sim_No_layer_preference,
  KO_sanction      = sim_KO_sanction,
  Enable_sink_strength    = sim_en_strength,
  KO_temporal      = sim_KO_temporal
)

species_order <- colnames(sim_BCM)
model_order <- c("BCM", "KO_space", "No_layer_preference", "KO_sanction", "Enable_sink_strength", "KO_temporal")

richness_df <- bind_rows(
  lapply(names(sim_cases_list), function(m) {
    df <- as.data.frame(sim_cases_list[[m]])[, species_order, drop = FALSE]

    tibble(
      Model = m,
      fig_id = seq_len(nrow(df)),
      richness = rowSums(df > 0, na.rm = TRUE)
    )
  })
)

richness_df$Model <- factor(richness_df$Model, levels = model_order)

ggplot(
  richness_df,
  aes(x = Model, y = richness, fill = Model)
) +
  geom_violin(trim = FALSE, alpha = 0.55, color = NA) +
  geom_boxplot(width = 0.12, outlier.alpha = 0.15, alpha = 0.9) +
  scale_fill_manual(values = c("#8dd3c7", "#fdb462",  "#C39BD3", "#fb8072", "#3498DB","#969696" )) +
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 21,
    size = 2.5,
    fill = "white",
    color = "black"
  ) +
  scale_y_continuous(breaks = sort(unique(richness_df$richness))) +
  labs(
    x = NULL,
    y = "Species richness per fig",
    title = "Richness distributions across simulation variants"
  ) +
  theme_classic(base_size = 12) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 30, hjust = 1),
    plot.title = element_text(face = "bold")
  )

heatmap_richness_all <- bind_rows(
  lapply(names(sim_cases_list), function(model_name) {

    df <- as.data.frame(sim_cases_list[[model_name]])[, species_order, drop = FALSE]

    # fig-level richness
    df$FigID <- seq_len(nrow(df))
    df$richness <- rowSums(df[, species_order] > 0, na.rm = TRUE)

    # long format
    df_long <- df %>%
      pivot_longer(
        cols = all_of(species_order),
        names_to = "Species",
        values_to = "Count"
      ) %>%
      mutate(Present = Count > 0)

    # proportion of figs at each richness level in which each species is present
    df_long %>%
      group_by(richness, Species) %>%
      summarise(
        N_present = sum(Present, na.rm = TRUE),
        Total_figs = n_distinct(FigID),
        Proportion = N_present / Total_figs,
        .groups = "drop"
      ) %>%
      mutate(Model = model_name)
  })
)

heatmap_richness_all <- heatmap_richness_all %>%
  mutate(
    Model = factor(Model, levels = model_order),
    Species = factor(Species, levels = species_order),
    richness = factor(richness, levels = sort(unique(richness)))
  )

ggplot(
  heatmap_richness_all,
  aes(x = richness, y = Species, fill = Proportion)
) +
  geom_tile(color = "white", linewidth = 0.4) +
  facet_wrap(~ Model, ncol = 3) +
  scale_fill_viridis_c(
    limits = c(0, 1),
    name = "Presence\nproportion"
  ) +
  labs(
    x = "Species richness per fig",
    y = NULL,
    #title = "Species occurrence structure across richness levels"
  ) +
  theme_bw(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    strip.background = element_rect(fill = "grey90", color = "grey40"),
    axis.text.x = element_text(angle = 0, hjust = 0.5),
    plot.title = element_text(face = "bold")
  )


```

# Other way: "knockout" single mechanism

## Disable ovary-layer structure

```{r, eval=FALSE}
sim_no_layering <- simulate_figwasp_community(
  ...,
  use_layering = FALSE,
  use_layer_preference = FALSE
)

```

## Disable species-specific layer preference

```{r, eval=FALSE}
sim_no_layer_preference <- simulate_figwasp_community(
  ...,
  use_layering = TRUE,
  use_layer_preference = FALSE
)

```

## Disable phase-specific success

```{r, eval=FALSE}

sim_no_phase <- simulate_figwasp_community(
  ...,
  use_egg_success_by_phase = FALSE
)

```