---
title: "Applying figsimR to other Ficus systems"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Applying figsimR to other Ficus systems}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Is figsimR restricted to Ficus racemosa?

No. The default worked example is parameterized for `Ficus racemosa`, but the number of simulated species is not hard-coded.

# What users need to provide

To adapt `figsimR` to another system, users need:

1. Species names
2. Guild assignments
3. Host–parasitoid links
4. Entry or oviposition schedules
5. Fecundity parameters
6. Layer preference or `"none"`
7. Optional fig-retention rules

# Two cases: simulation for other "fig" systems
To demonstrate this flexibility, here, we tested the package using two additional user-defined examples: a minimal two-species community and a ten-species community that includes multiple pollinating fig wasp species. In both cases, the species names and interaction structures were user-defined. These examples show that figsimR can accommodate both simplified and more complex fig-fig wasp communities. 

## function for parameter check
Let define a parameter check function first

```{r parameter_check_function}

validate_figsim_parameter_list <- function(parameter_list) {

  required_components <- c(
    "entry_mu",
    "entry_size",
    "fecundity_mean",
    "fecundity_dispersion",
    "egg_success_prob",
    "egg_success_prob_by_phase",
    "layer_preference",
    "max_entry_table",
    "parasitism_prob",
    "entry_priority",
    "interaction_matrix",
    "interaction_weight",
    "species_roles"
  )

  missing_components <- setdiff(required_components, names(parameter_list))
  if (length(missing_components) > 0) {
    stop(
      "Missing required components: ",
      paste(missing_components, collapse = ", ")
    )
  }

  species_roles <- parameter_list$species_roles
  species_names <- names(species_roles$guild)

  if (length(species_names) == 0) {
    stop("species_roles$guild must be a named vector.")
  }

  # Check species-indexed numeric vectors
  species_vectors <- c(
    "entry_mu",
    "entry_size",
    "fecundity_mean",
    "fecundity_dispersion",
    "egg_success_prob",
    "max_entry_table"
  )

  for (v in species_vectors) {
    missing_species <- setdiff(species_names, names(parameter_list[[v]]))
    extra_species <- setdiff(names(parameter_list[[v]]), species_names)

    if (length(missing_species) > 0) {
      stop(v, " is missing species: ", paste(missing_species, collapse = ", "))
    }

    if (length(extra_species) > 0) {
      warning(v, " contains extra species: ", paste(extra_species, collapse = ", "))
    }
  }

  # Check hosts and parasitoid lists
  if (!all(species_names %in% names(species_roles$hosts))) {
    stop("species_roles$hosts must contain all species.")
  }

  if (!all(species_names %in% names(species_roles$parasitoid))) {
    stop("species_roles$parasitoid must contain all species.")
  }

  all_hosts <- unique(unlist(species_roles$hosts))
  all_parasitoids <- unique(unlist(species_roles$parasitoid))

  invalid_hosts <- setdiff(all_hosts, species_names)
  invalid_parasitoids <- setdiff(all_parasitoids, species_names)

  if (length(invalid_hosts) > 0) {
    stop("Unknown host species: ", paste(invalid_hosts, collapse = ", "))
  }

  if (length(invalid_parasitoids) > 0) {
    stop("Unknown parasitoid species: ", paste(invalid_parasitoids, collapse = ", "))
  }

  # Check entry priority
  entry_species <- unique(unlist(parameter_list$entry_priority))
  missing_from_priority <- setdiff(species_names, entry_species)
  invalid_priority_species <- setdiff(entry_species, species_names)

  if (length(missing_from_priority) > 0) {
    warning(
      "These species are not included in entry_priority: ",
      paste(missing_from_priority, collapse = ", ")
    )
  }

  if (length(invalid_priority_species) > 0) {
    stop(
      "entry_priority contains unknown species: ",
      paste(invalid_priority_species, collapse = ", ")
    )
  }

  # Check interaction matrix
  interaction_matrix <- parameter_list$interaction_matrix

  if (!is.matrix(interaction_matrix)) {
    stop("interaction_matrix must be a matrix.")
  }

  if (!all(species_names %in% rownames(interaction_matrix)) ||
      !all(species_names %in% colnames(interaction_matrix))) {
    stop("interaction_matrix rownames and colnames must include all species.")
  }

  # Check layer preference
  if (!all(species_names %in% names(parameter_list$layer_preference))) {
    stop("layer_preference must contain all species.")
  }

  # Check egg_success_prob_by_phase
  if (!all(species_names %in% names(parameter_list$egg_success_prob_by_phase))) {
    stop("egg_success_prob_by_phase must contain all species.")
  }

  message("Parameter list passed all checks.")
  invisible(TRUE)
}

```


## ten-species community with two pollinators

```{r simulations}

library(figsimR)
set.seed(42)

# define parameter list
custom_species <- c(
  "Pollinator_A",
  "Pollinator_B",
  "Galler_A",
  "Galler_B",
  "Galler_C",
  "Parasitoid_A",
  "Parasitoid_B",
  "Parasitoid_C",
  "Hyperparasitoid_A",
  "Hyperparasitoid_B"
)

custom_roles <- list(
  guild = c(
    Pollinator_A      = "pollinator",
    Pollinator_B      = "pollinator",
    Galler_A          = "galler",
    Galler_B          = "galler",
    Galler_C          = "galler",
    Parasitoid_A      = "parasitoid",
    Parasitoid_B      = "parasitoid",
    Parasitoid_C      = "parasitoid",
    Hyperparasitoid_A = "parasitoid",
    Hyperparasitoid_B = "parasitoid"
  ),

  hosts = list(
    Pollinator_A      = character(0),
    Pollinator_B      = character(0),
    Galler_A          = character(0),
    Galler_B          = character(0),
    Galler_C          = character(0),
    Parasitoid_A      = c("Galler_A"),
    Parasitoid_B      = c("Galler_B", "Galler_C"),
    Parasitoid_C      = c("Pollinator_A"),
    Hyperparasitoid_A = c("Parasitoid_A"),
    Hyperparasitoid_B = c("Parasitoid_B", "Parasitoid_C")
  ),

  parasitoid = list(
    Pollinator_A      = c("Parasitoid_C"),
    Pollinator_B      = character(0),
    Galler_A          = c("Parasitoid_A"),
    Galler_B          = c("Parasitoid_B"),
    Galler_C          = c("Parasitoid_B"),
    Parasitoid_A      = c("Hyperparasitoid_A"),
    Parasitoid_B      = c("Hyperparasitoid_B"),
    Parasitoid_C      = c("Hyperparasitoid_B"),
    Hyperparasitoid_A = character(0),
    Hyperparasitoid_B = character(0)
  )
)

custom_parameter_list <- list(
  entry_mu = c(
    Pollinator_A      = 8,
    Pollinator_B      = 4,
    Galler_A          = 5,
    Galler_B          = 4,
    Galler_C          = 4,
    Parasitoid_A      = 3,
    Parasitoid_B      = 3,
    Parasitoid_C      = 2,
    Hyperparasitoid_A = 1.5,
    Hyperparasitoid_B = 1.5
  ),

  entry_size = c(
    Pollinator_A      = 6,
    Pollinator_B      = 5,
    Galler_A          = 5,
    Galler_B          = 5,
    Galler_C          = 5,
    Parasitoid_A      = 4,
    Parasitoid_B      = 4,
    Parasitoid_C      = 4,
    Hyperparasitoid_A = 3,
    Hyperparasitoid_B = 3
  ),

  fecundity_mean = c(
    Pollinator_A      = 80,
    Pollinator_B      = 70,
    Galler_A          = 25,
    Galler_B          = 22,
    Galler_C          = 20,
    Parasitoid_A      = 8,
    Parasitoid_B      = 8,
    Parasitoid_C      = 7,
    Hyperparasitoid_A = 5,
    Hyperparasitoid_B = 5
  ),

  fecundity_dispersion = c(
    Pollinator_A      = 1.2,
    Pollinator_B      = 1.2,
    Galler_A          = 1.5,
    Galler_B          = 1.5,
    Galler_C          = 1.5,
    Parasitoid_A      = 2,
    Parasitoid_B      = 2,
    Parasitoid_C      = 2,
    Hyperparasitoid_A = 2,
    Hyperparasitoid_B = 2
  ),

  egg_success_prob = c(
    Pollinator_A      = 0.9,
    Pollinator_B      = 0.85,
    Galler_A          = 0.75,
    Galler_B          = 0.7,
    Galler_C          = 0.7,
    Parasitoid_A      = 0.6,
    Parasitoid_B      = 0.6,
    Parasitoid_C      = 0.55,
    Hyperparasitoid_A = 0.5,
    Hyperparasitoid_B = 0.5
  ),

  egg_success_prob_by_phase = list(
    Pollinator_A      = c(phase2 = 0.9),
    Pollinator_B      = c(phase2 = 0.8),
    Galler_A          = c(phase1 = 0.7),
    Galler_B          = c(phase1 = 0.7, phase2 = 0.6),
    Galler_C          = c(phase2 = 0.7),
    Parasitoid_A      = c(phase2 = 0.6),
    Parasitoid_B      = c(phase2 = 0.6, phase3 = 0.6),
    Parasitoid_C      = c(phase2 = 0.5),
    Hyperparasitoid_A = c(phase3 = 0.5),
    Hyperparasitoid_B = c(phase3 = 0.5)
  ),

  layer_preference = list(
    Pollinator_A      = c(core = 0.7, mid = 0.2, outer = 0.1),
    Pollinator_B      = c(core = 0.6, mid = 0.3, outer = 0.1),
    Galler_A          = c(core = 0.5, mid = 0.3, outer = 0.2),
    Galler_B          = c(core = 0.4, mid = 0.4, outer = 0.2),
    Galler_C          = c(core = 0.3, mid = 0.4, outer = 0.3),
    Parasitoid_A      = c(core = 0.2, mid = 0.4, outer = 0.4),
    Parasitoid_B      = c(core = 0.2, mid = 0.3, outer = 0.5),
    Parasitoid_C      = c(core = 0.3, mid = 0.3, outer = 0.4),
    Hyperparasitoid_A = c(core = 0.1, mid = 0.3, outer = 0.6),
    Hyperparasitoid_B = c(core = 0.1, mid = 0.3, outer = 0.6)
  ),

  max_entry_table = setNames(rep(20, length(custom_species)), custom_species),

  parasitism_prob = c(
    Parasitoid_A      = 0.85,
    Parasitoid_B      = 0.80,
    Parasitoid_C      = 0.75,
    Hyperparasitoid_A = 0.60,
    Hyperparasitoid_B = 0.60
  ),

  entry_priority = list(
    phase1 = c("Galler_A", "Galler_B"),
    phase2 = c(
      "Pollinator_A",
      "Pollinator_B",
      "Galler_B",
      "Galler_C",
      "Parasitoid_A",
      "Parasitoid_B",
      "Parasitoid_C"
    ),
    phase3 = c(
      "Parasitoid_B",
      "Hyperparasitoid_A",
      "Hyperparasitoid_B"
    )
  ),

  interaction_matrix = matrix(
    0,
    nrow = length(custom_species),
    ncol = length(custom_species),
    dimnames = list(custom_species, custom_species)
  ),

  interaction_weight = 0,

  species_roles = custom_roles
)

```

## check parameter for the community with ten wasp species

```{r parameter_check}
validate_figsim_parameter_list(custom_parameter_list)

```

Everthing looks great, let's simulate the community!

```{r simulation}

set.seed(123)

custom_sim <- do.call(
  simulate_figwasp_community,
  c(
    list(
      num_figs = 50,
      seed = 123,
      use_layering = TRUE,
      use_layer_preference = TRUE,
      use_sink_strength = TRUE,
      enable_drop = FALSE
    ),
    custom_parameter_list
  )
)

custom_summary <- custom_sim$summary

head(custom_summary)

```

# two-species community 
Here, we have a minimal two-species example.

```{r simulations_two_species}
two_species <- c("Pollinator_A", "Galler_A")

two_roles <- list(
  guild = c(
    Pollinator_A = "pollinator",
    Galler_A     = "galler"
  ),
  hosts = list(
    Pollinator_A = character(0),
    Galler_A     = character(0)
  ),
  parasitoid = list(
    Pollinator_A = character(0),
    Galler_A     = character(0)
  )
)

two_parameter_list <- list(
  entry_mu = c(
    Pollinator_A = 8,
    Galler_A     = 5
  ),

  entry_size = c(
    Pollinator_A = 6,
    Galler_A     = 5
  ),

  fecundity_mean = c(
    Pollinator_A = 80,
    Galler_A     = 25
  ),

  fecundity_dispersion = c(
    Pollinator_A = 1.2,
    Galler_A     = 1.5
  ),

  egg_success_prob = c(
    Pollinator_A = 0.9,
    Galler_A     = 0.7
  ),

  egg_success_prob_by_phase = list(
    Pollinator_A = c(phase2 = 0.9),
    Galler_A     = c(phase1 = 0.7)
  ),

  layer_preference = list(
    Pollinator_A = c(core = 0.7, mid = 0.2, outer = 0.1),
    Galler_A     = c(core = 0.4, mid = 0.4, outer = 0.2)
  ),

  max_entry_table = c(
    Pollinator_A = 20,
    Galler_A     = 20
  ),

  parasitism_prob = c(),

  entry_priority = list(
    phase1 = c("Galler_A"),
    phase2 = c("Pollinator_A")
  ),

  interaction_matrix = matrix(
    0,
    nrow = length(two_species),
    ncol = length(two_species),
    dimnames = list(two_species, two_species)
  ),

  interaction_weight = 0,

  species_roles = two_roles
)

validate_figsim_parameter_list(two_parameter_list)

two_sim <- do.call(
  simulate_figwasp_community,
  c(
    list(
      num_figs = 100,
      seed = 123,
      use_layering = TRUE,
      use_layer_preference = TRUE,
      enable_drop = TRUE
    ),
    two_parameter_list
  )
)

two_summary <- two_sim$summary
head(two_summary)

```

# Practical limitations
Use this package to other Ficus-fig wasp systems, the prerequisite is that you need to prepare the input data following the package guidelines, especially species roles and guilds, basic biological information, such as expected oviposition or egg-laying rates, interactions among species, host-parasitoid relationships. In fact, for many fig wasp communities, this information is scattered across different publications or remains unclear, which may limit practical application. However, this is a limitation of available biological information rather than a restriction of the package.